\usepackage{hyperref}

\newcommand{\refashp}{
{\em AHFS\textsuperscript \textregistered Pharmacologic/Therapeutic Classification\textsuperscript \textcopyright} used with permission. \textcopyright\ 2017, the American Society of Health-System Pharmacists, Inc. (ASHP). The Data is a part of the {\em AHFS Drug Information\textsuperscript \textregistered}; ASHP is not responsible for the accuracy of transpositions from the original context.
}

\newcommand{\refndc}{
U.S. Food \& Drug Administration.
National Drug Code Directory [Internet; cited 2019 Feb 19];
Available from: \url{https://www.fda.gov/Drugs/InformationOnDrugs/ucm142438.htm}
}

\newcommand{\refhistoricalndc}{
Research Improving People's Lives.
Assembling a Historical National Drug Code Directory from the Internet Archive [Internet; cited 2019 Feb 19];
Available from: \url{https://github.com/ripl-org/historical-ndc}
}

\newcommand{\refamdg}{
Agency Medical Directors' Group. Interagency Guideline on Prescribing Opioids for Pain.
Olympia, WA: 2015 [cited 2019 Feb 19].
Available from: \url{http://www.agencymeddirectors.wa.gov/Files/2015AMDGOpioidGuideline.pdf}
}

\newcommand{\refdowell}{
Dowell D, Haegerich TM, Chou R. CDC Guideline for Prescribing Opioids for Chronic Pain — United States, 2016. MMWR Recomm Rep [Internet]. 2016 [cited 2019 Feb 19];65. Available from: \url{https://www.cdc.gov/mmwr/volumes/65/rr/rr6501e1.htm}
}

\newcommand{\refrice}{
Rice JB, White AG, Birnbaum HG, Schiller M, Brown DA, Roland CL. A model to identify patients at risk for prescription opioid abuse, dependence, and misuse. Pain Med. 2012;13(9):1162–1173. 
}

\newcommand{\refhylan}{
Hylan TR, Von Korff M, Saunders K, Masters E, Palmer RE, Carrell D, et al. Automated Prediction of Risk for Problem Opioid Use in a Primary Care Setting. J Pain. 2015 Apr;16(4):380–7. 
}

\newcommand{\refdufour}{
Dufour R, Mardekian J, Pasquale MK, Schaaf D, Andrews GA, Patel NC. Understanding predictors of opioid abuse: predictive model development and validation. Am J Pharm Benefits. 2014;6(5):208–216. 
}

\newcommand{\refjones}{
Jones CM. Heroin use and heroin use risk behaviors among nonmedical users of prescription opioid pain relievers – United States, 2002–2004 and 2008–2010. Drug Alcohol Depend. 2013 Sep;132(1–2):95–100. 
}

\newcommand{\refcarrell}{
Carrell DS, Cronkite D, Palmer RE, Saunders K, Gross DE, Masters ET, et al. Using natural language processing to identify problem usage of prescription opioids. Int J Med Inform. 2015 Dec;84(12):1057–64. 
}

\newcommand{\refabadi}{
Abadi M, Barham P, Chen J, Chen Z, Davis A, Dean J, et al. TensorFlow: A System for Large-Scale Machine Learning. In: 12th {USENIX} Symposium on Operating Systems Design and Implementation ({OSDI} 16). 2016 [cited 2019 Feb 19]. p. 265–83. Available from: \url{https://www.usenix.org/conference/osdi16/technical-sessions/presentation/abadi}
}

\newcommand{\refkingma}{
Kingma DP, Ba J. Adam: A Method for Stochastic Optimization. arXiv:14126980 [Internet]. 2014 Dec 22 [cited 2019 Feb 19]; Available from: \url{http://arxiv.org/abs/1412.6980}
}

\newcommand{\refsrivastava}{
Srivastava N, Hinton G, Krizhevsky A, Sutskever I, Salakhutdinov R. Dropout: A Simple Way to Prevent Neural Networks from Overfitting. J Mach Learn Res. 2014 Jun 14;15:1929–58. 
}

\newcommand{\refbarocas}{
Barocas JA, White LF, Wang J, Walley AY, LaRochelle MR, Bernson D, et al. Estimated Prevalence of Opioid Use Disorder in Massachusetts, 2011–2015: A Capture–Recapture Analysis. Am J Public Health. 2018 Oct 25;108(12):1675–81. 
}

\newcommand{\refhastings}{
Hastings JS, Howison M, Lawless T, Ucles J, White P. Integrating Administrative Data for Policy Insights. OSF Preprints [Internet]. 2018 Jul 19 [cited 2018 Aug 23]; Available from: \url{https://osf.io/hdv3c/}
}

\newcommand{\refhochreiter}{
Hochreiter S, Schmidhuber J. Long Short-Term Memory. Neural Computation. 1997 Nov 1;9(8):1735–80. 
}

\newcommand{\reftaddy}{
Taddy M. One-step estimator paths for concave regularization. arXiv:13085623 [Internet]. 2016 May 1 [cited 2019 Feb 27]; Available from: \url{http://arxiv.org/abs/1308.5623}
}

\newcommand{\refchollet}{
Chollet F, et al. Keras: The Python Deep Learning library [Internet; cited 2019 Feb 27]; Available from: \url{https://keras.io/}
}

\newcommand{\refkleinberg}{
Kleinberg J, Ludwig J, Mullainathan S, Obermeyer Z. Prediction Policy Problems. Am Econ Rev. 2015 May;105(5):491–5. 
}

\newcommand{\refbach}{
Bach FR. Bolasso: Model Consistent Lasso Estimation Through the Bootstrap. In: Proceedings of the 25th International Conference on Machine Learning [Internet]. New York, NY, USA: ACM; 2008 [cited 2018 Feb 19]. p. 33–40. (ICML 08). Available from: \url{http://doi.acm.org/10.1145/1390156.1390161}
}